Meta-analysis

### 2019-09-02 05_MetaAnalysis.Rmd
Exploring between trial variation with fungicide use .... However this does not find the means of each trial so it is not effectivley measureing the correct aggregated data. This is because it is taking the means of each fungicide treatment within trial, regardless of row.spacing or spray applications

```{r Fungicides}
unique(PM_MB_means$Fungicide)
PM_MB_means %>%
   group_by(Fungicide,Trial_ref) %>%
   summarise() %>%
   count(sort = T) %>%
   rename(Trials = n) %>%
   kable()

@@

### Fungicide Doses
All trials that used Tebeconazole used approimately the same dose. dose of the active ingredient ranged from 62.35 grams per hectare to 60 grams per hectare. 
```{r Tebe_dose}
PM_MB_means %>%
   filter(Fungicide == "Tebeconazole") %>%
   select(Trial_ref, Year, Location, first_sign_disease, Dose.ai.ha., total_Fungicide) %>%
   kable()
# why are there zeros
```

@@

@@

```
Were there any statistical diference between all row spacing or only some?  
Can we pool certain row spacings that have no significant difference?

@@

```{r variance}
   PM_MB_means %>%
   filter(Fungicide == "Tebeconazole",
          row_spacing == 0.75) %>%
   group_by(Trial_ref, Y_error.type) %>%
   summarise(Tebe_Treatments = length(Y_error.type))
```

@@

The trial, `mung1112/02` uses Least squre differences to describe the variation within the experiment. The following code attempts to convert this to sampling variance as per the method in [Nugugi et.al (2011)](https://apsjournals.apsnet.org/doi/10.1094/PHYTO-08-10-0221). Ideas for using a T-critical value of 1.697 came from reading a [statisics-how-to website](https://www.statisticshowto.datasciencecentral.com/how-to-calculate-the-least-significant-difference-lsd/). A [table of T-critical values](https://www.statisticshowto.datasciencecentral.com/tables/t-distribution-table/) was consulted where 30 degrees of freedom within expeiment was used to find the 'T-crit' value of 1.697.

@@

>>>>

```{r Fungicides}
#unique(PM_MB_means$Fungicide)
PM_MB_means %>%
   group_by(Fungicide,Trial_ref) %>%
   summarise() %>%
   count(sort = T) %>%
   rename(Trials = n) %>%
   kable()

@@

Preliminary analysis of Fungicides show there is a difference the effect of Fungicide in proportion of yield gained

### Fungicide Doses
All trials that used Tebeconazole used approimately the same dose. dose of the active ingredient ranged from 62.35 grams per hectare to 60 grams per hectare. 
```{r Tebe_dose}
PM_MB_means %>%
   filter(Fungicide == "Tebeconazole") %>%
   select(Trial_ref, Year, Location, first_sign_disease, Dose.ai.ha., total_Fungicide) %>%
   kable()
# why are there zeros - FIXED
```

@@

PM_MB_means %>%
   filter(Fungicide == "propiconazole") %>%
   group_by(row_spacing,Trial_ref) %>%
   summarise() %>%
   count() %>%
   rename(Trials = n) %>%
   kable()

@@

```
Were there any statistical diference between all row spacing or only some?  
Can we pool certain row spacings that have no significant difference?
From the preliminary analysis, graphs seem to imply that if there is a lower overall yeild there is no effect of row spacing on yield. However if the average yield is more than approximatley 0.6 - 1 T/Ha then smaller row spacing has the potenial to provide greater yield.

@@

```{r variance}
   PM_MB_means %>%
   filter(Fungicide == "Tebeconazole",
          row_spacing == 0.75) %>%
   group_by(Trial_ref, Location, Y_error.type) %>%
   summarise(Tebe_Treatments = length(Y_error.type))

   PM_MB_means %>%
   filter(Fungicide == "propiconazole",
          row_spacing == 0.75) %>%
   group_by(Trial_ref, Location, Y_error.type) %>%
   summarise(Tebe_Treatments = length(Y_error.type))
colnames(PM_MB_means)

@@

The trial, `mung1112/02` uses Least square differences to describe the variation within the experiment. The following code attempts to convert this to sampling variance as per the method in [Nugugi et.al (2011)](https://apsjournals.apsnet.org/doi/10.1094/PHYTO-08-10-0221). Ideas for using a T-critical value of 1.697 came from reading a [statisics-how-to website](https://www.statisticshowto.datasciencecentral.com/how-to-calculate-the-least-significant-difference-lsd/). A [table of T-critical values](https://www.statisticshowto.datasciencecentral.com/tables/t-distribution-table/) was consulted where 30 degrees of freedom within expeiment was used to find the 'T-crit' value of 1.697.

@@

Emerson proposed I look at the between trial variation
```{r between_trial_variation}
levels(factor(PM_MB_means$Y_error.type))

PM_MB_means.SV <- PM_MB_means[PM_MB_means$Y_error.type == "SamplingVariance",]

meta_mean.GY <- mean(PM_MB_means.SV$grain_yield.t.ha.,na.rm = TRUE)

PM_MB_means_T <- PM_MB_means %>%
   group_by(Trial_ref, Fungicide) %>%
   summarise(trial_mean = mean(grain_yield.t.ha.,na.rm = TRUE),
             BW_trial_variance = sd(grain_yield.t.ha.,na.rm = TRUE)^2)
PM_MB_means_T

summary(lm(BW_trial_variance ~ trial_mean  Fungicide, data = PM_MB_means_T))
summary(lm(BW_trial_variance ~ trial_mean, data = subset(PM_MB_means_T, Fungicide == "Tebeconazole")))
summary(lm(BW_trial_variance ~ trial_mean, data = subset(PM_MB_means_T, Fungicide == "propiconazole")))

plot(BW_trial_variance ~ trial_mean, data = PM_MB_means_T)
abline(-0.01356,0.03076)
points(BW_trial_variance ~ trial_mean, data = subset(PM_MB_means_T, Fungicide == "Tebeconazole"),col = "red", pch = 3)
abline(-0.005162, 0.019892, col = "red")
points(BW_trial_variance ~ trial_mean, data = subset(PM_MB_means_T, Fungicide == "propiconazole"),col = "blue", pch = 3)
abline(-0.03962, 0.05454, col = "blue")

lm_within <- lm(BW_trial_variance ~ trial_mean * Trial_ref + Fungicide,
                    data = PM_MB_means_T)
summary(lm_within) # Not accurate in predicting TrialVariance from trial means

lm_within2 <- lm(BW_trial_variance ~ trial_mean + Trial_ref + Fungicide,
                    data = PM_MB_means_T)
summary(lm_within2) # Not accurate in predicting TrialVariance from trial means

lmer_within_1 <- lmer(BW_trial_variance ~ trial_mean + (1|Trial_ref/Fungicide),
                    data = PM_MB_means_T)
# unable to nest Fungicide under trial ref

lmer_within_1 <- lmer(BW_trial_variance ~ trial_mean + Fungicide + (1|Trial_ref),
                    data = PM_MB_means_T)
# not accurate  for predicting TrialVariance

summary(lmer_within_1)
